### 2013-09-29 tex/scam/rebuttal_nips2013.txt

We thank the reviewers for their thoughtful reviews. We would like to point out that this paper is not solely theoretical; the scalable practical optimization algorithm we develop is also a major contribution.

Reviewer 1:
(1) Thanks for pointing out these references. We are aware of these prior works and thought that a comprehensive comparison is more appropriate for a journal version.

(2) Yes, with the L_inf bound on f^*, the alpha decays with s. We did not investigate this further because this paper studies how n can scale with p as both go to infinity; we think of s as a bounded quantity. The key contribution and the most interesting aspect of the theorem is that the ambient dimension can scale exponentially in n; the actual dimension s is usually very small in practice. This is definitely a point we would clarify in the future revisions.

(3) E[f(X)|x_k] is a notational short-hand; it is not "an elementary mistake in math." Lemma 6.1 does not need or have the product distribution assumption; Proposition 6.1 uses it. Theorem 2.1 does assume that the distribution has a density; that was an oversight on our part. Please do let us know if there are other mistakes that you found.

Reviewer 5:
(1) The present version is not wrong. Uniqueness is obvious from the fact that the objective in Lemma 6.1 is a sum of squares and is therefore strongly convex in f_k(x_k) for every f_k(x_k). Do you have a counterexample in mind?

(2) The claim of Theorem 4.3 is not nonsense; it requires that s does not tend to infinity but it is otherwise correct. If we assume that the covariates are independent, then any affine function have support identifiability (sparsistency) even if the ambient dimension p ~ exp(n^c) for c < 1; no additional separation assumptions are needed.

(3) Theorem 2.1 is only one of the main contributions of the paper.

(4) The result announced in the introduction is, as stated in the introduction, proved in the two references [5][6].

Reviewer 7:
(1) Thanks for pointing out the two references. We would definitely add these to a longer version of this paper.

### 2013-09-29 tex/scam/appendix.tex
first init

\documentclass{article}
\usepackage{minx_math}
\usepackage{framed, mathtools, epstopdf,subfigure}

% eqn:alternate_opt

\begin{document}

\section{Setting and Notations}

\textbf{Setting:}
\begin{packed_enum}
\item Let $Y' = f_0(X) + \epsilon$ where $f_0$ is the true function and $\epsilon$ is noise.  Given $n$ samples $Y'^{(1)},...,Y'^{(n)}$, we input into our optimization $Y = Y' - \bar{Y}'$.
\item Let $\mathcal{X} = [-b, b]^p$. Let $\mathcal{P}$ be a distribution on $\mathcal{X}$. Let $X^{(1)},..., X^{(n)} $ be independent samples from $\mathcal{P}$. 
\item Let $S \subset \{1,...,p\}$ denote the set of relevant variables, that is, $f_0(X) = f_0(X_S)$ and let $s \coloneqq |S|$.
\end{packed_enum}

\textbf{Assumptions:}
\begin{packed_enum}
\item[A1] Suppose that $X_S, X_{S^c}$ are independent.
\item[A1'] Suppose A1 is true and $\{ X_k \}_{k \in S}$ are all independent. 
\item[A2] Suppose that $\|f_0\|_\infty \leq B$.
\item[A2'] Suppose that A2 is true and $f_0$ is convex and $L$-$Lipschitz$.
\item[A3] Suppose $\epsilon$ is mean-zero subgaussian, independent of $X$, with subgaussian scale $\sigma$.
\end{packed_enum}

\textbf{Notation:}
$\mathbf{1}_n$ is an all-ones vector of dimension $n$. If $X \in \R^p$ and $S \subset \{1,...,p\}$, then $X_S$ is a subvector of $X$ restricted to coordinates in $S$. Let $v \in \R^n$, then $v_{(1)}$ denotes the largest coordinate of $v$ in magnitude, $v_{(j)}$ denotes the $j$-th largest. \\

\subsection{Reformulation}

Let $x_{s(1)} ,..., x_{s(n)}$ be the $n$ samples arranged from small to large. Define $\hat{\beta}_{s1}$ as $\frac{\hat{f}_s(x_{s(2)}) - \hat{f}_s(x_{s(1)})}{x_{s(2)} - x_{s(1)}}$.\\

Then  
\begin{align*}
\hat{f}_s(x_{s(1)}) &= \hat{f}_s(x_{s(1)})  \qquad \trm{ constrained by centering}\\
\hat{f}_s(x_{s(2)}) &= \hat{f}_s(x_{s(1)}) + \hat{\beta}_{s1} (x_{s(2)}-x_{s(1)} )\\
\hat{f}_s(x_{s(t)}) &= \hat{f}_s(x_{s(1)}) + \sum_{t' = 1}^{t-1} \hat{\beta}_{s t'} ( x_{s (t'+1)} - x_{s (t')}) 
\end{align*}

We thus define the notation $\hat{f}_s(x_{si}) = c_s + \hat{\beta}_s^\tran D_{si}$ where $D_{si} \in \R^{n-1}$, and is a vector
\[
D_{si} = [ x_{s(2)} - x_{s(1)}, x_{s(3)} - x_{s(2)}, ..., x_{s(t)} - x_{s(t-1)}, 0, ..., 0] \qquad \trm{ where } t = order(i)
\]

And we have the constraint that $\sum_{i=1}^n \hat{f}_s(x_{si}) = n c_s + \sum_{i=1}^n \hat{\beta}_s^\tran D_{si} = 0$, therefore, $c_s = - \left( \frac{1}{n} \sum_{i=1}^n  D_{si} \right)^\tran \hat{\beta}_s$.

\textbf{Some additional transformation.} Let's define $\hat{d}_{s(i)}$ as the gradient increment. $\hat{d}_{s(1)} = \hat{\beta}_{s(1)}$, and $\hat{d}_{s(2)} = \hat{\beta}_{s(2)} - \hat{\beta}_{s(1)}$. The convexity constraint translates to the constraint that $\hat{d}_{s(i)} \geq 0$ for all $i > 1$.\\

$\hat{\beta}_{s(i)} = \sum_{j \leq i} \hat{d}_{s(i)}$.

\[
\hat{f}_s(x_{s(2)}) = \hat{f}_s(x_{s(1)}) + \hat{d}_{s(1)} ( x_{s(2)} - x_{s(1)})
\]

\begin{align*}
\hat{f}_s(x_{s(3)}) &= \hat{f}_s(x_{s(2)}) + \hat{\beta}_{s(2)} ( x_{s(3)} - x_{s(2)}) \\
 &= \hat{f}_s({x_{s(1)}}) + \hat{d}_{s(1)} ( x_{s(2)} - x_{s(1)}) + (\hat{d}_{s(2)}+\hat{d}_{s(1)}) (x_{s(3)} - x_{s(2)}) \\
 &= \hat{f}_s({x_{s(1)}}) + \hat{d}_{s(1)} (x_{s(3)}-x_{s(1)} ) + \hat{d}_{s(2)} (x_{s(3)}-x_{s(2)} )
\end{align*}

\[
\hat{f}_s(x_{s(i)}) = \hat{f}_s({x_{s(1)}}) +\hat{d}_{s(1)} ( x_{s(i)} - x_{s(1)}) + \hat{d}_{s(2)} ( x_{s(i)} - x_{s(2)}) + ... + \hat{d}_{s(i-1)} ( x_{s(i)} - x_{s(i-1)})
\]

Define $\Delta(j, x_{si}) = 0$ if $\trm{order}(i) \leq j$, $x_{si} - x_{s(j)}$ else. The $j$ ranges from $1$ to $n-1$. With this definition, we can re-write

\[
\hat{f}_s(x_{si}) = \hat{d}_{s}^\tran \Delta(x_{si}) \qquad \trm{where $\Delta(x_{si}) \in \R^{n-1}$.}
\]

With the simple constraint that all $\hat{d}_{si} \geq 0$ for $i > 1$.\\

\begin{align}
\min_{\{d_k, c_k\}}& \frac{1}{2n} \| Y - \sum_{k=1}^p ( \Delta_k d_k - c_k \mathbf{1}_n) \|_2^2 + \lambda_n \sum_{k=1}^p \| d_k \|_1 & \label{opt:alternate_opt} \\
\trm{s.t. $\forall k$, }  & d_{k2}, ..., d_{k(n-1)} \geq 0 	\qquad &\trm{(convexity)} \nonumber \\ 
	& c_k = \frac{1}{n} \mathbf{1}_n^\tran \Delta_k d_k 	\qquad &\trm{(centering)} \nonumber \\
	& -B \mathbf{1}_n \leq \Delta_k d_k + c_k \mathbf{1}_n \leq B \mathbf{1}_n  \qquad &\trm{(boundedness*)} \nonumber \\
	& \|d_k\|_1 \leq L & \trm{(smoothness*)} \nonumber
\end{align}

We will impose the boundness and smoothness constraints only in our theoretical analysis when we control the rate of false negatives.

\begin{align}
\min_{\{d_k, c_k\}}& \frac{1}{2n} \| Y - \sum_{k \in S} ( \Delta_k d_k - c_k \mathbf{1}_n) \|_2^2 + \lambda_n \sum_{k=1}^p \| d_k \|_1 & \label{opt:restricted_alternate_opt} \\
\trm{s.t. $\forall k \in S$, }  & d_{k2}, ..., d_{k(n-1)} \geq 0 	\qquad &\trm{(convexity)} \nonumber \\ 
	& c_k = \frac{1}{n} \mathbf{1}_n^\tran \Delta_k d_k 	\qquad &\trm{(centering)} \nonumber \\
	& -B \mathbf{1}_n \leq \Delta_k d_k + c_k \mathbf{1}_n \leq B \mathbf{1}_n  \qquad &\trm{(boundedness*)} \nonumber \\
	& \|d_k\|_1 \leq L & \trm{(smoothness*)} \nonumber
\end{align}

In the proof, we will reason with the solution of the optimization \ref{opt:alternate_opt} when we restricted $k$ to be only in the subset $S$. This is of course a theoretical construct only and we refer to it as \emph{restricted regression}.\\

For a function $g : \R^s \rightarrow \R$, define $\hat{R}_s(g) \coloneqq \| f_0 + w - g \|_n^2$ and define $R_s(g) \coloneqq \E | f_0(X)  + w - g(X) |^2$.

For an additive function $g$, define $\rho_n(g) = \sum_{k=1}^s \| \partial g_k \|_\infty$. Because we use outer approximation in our optimization program, we define $\ds \| \partial g_k\|_\infty \coloneqq \max_{i=1,...,n-1} |\frac{ g_k(X^{(i)}) - g_k(X^{(i+1)})}{ X^{(i)} - X^{(i+1)}}|$.

Let $\mathcal{C}^s[b,B,L]$ be the set of additive functions with $s$ components each of which is in $\mathcal{C}[b,B,L]$. 
\[
\mathcal{C}^s[b,B,L] \coloneqq \{ f : \R^s \rightarrow \R \,:\, f = \sum_{k=1}^s f_k(x_k), \, f_k \in \mathcal{C}[b,B,L] \}
\]

\section{Functions Which Are Not Additively Faithful}

\textbf{Example 1:}
\[
f(x_1, x_2) = \sin( 2\pi x_1) \sin( 2 \pi x_2) \qquad \trm{ for } (x_1, x_2) \in [0,1]^2
\]
Note that for all $x_1$, $\int_{x_2} f(x_1, x_2) d x_2 = 0$ and also, for all $x_2$, $\int_{x_1} f(x_1, x_2) d x_1 = 0$.
An additive model would set $f_1 = 0$ and $f_2 = 0$.

\begin{figure}[htp]
\subfigure[Example 1]{\includegraphics[scale=0.5]{../code/figs/sine_wave_funct.eps}}
\subfigure[Example 2]{\includegraphics[scale=0.4]{../code/figs/rising_slope_funct.eps}}
\end{figure}

\textbf{Example 2:}
\[
f(x_1, x_2) = x_1 x_2 \qquad \trm{ for } x_1 \in [-1,1], x_2 \in [0,1]
\]
Note that for all $x_2$, $\int_{x_1} f(x_1, x_2) d x_1 = 0$, therefore, we expect $f_2 = 0$ under the additive model.

This function, for every fixed $x_2$, is a zero-intercept linear function of $x_1$ with slope exactly $x_2$.

\section{Convex Functions are Additively Faithful}

Let $\mu$ be a probability measure on $C=[0,1]^s$, $f(x)$ be a multivariate function on $C$. We say that $f$ depends on coordinate $i$ if there exist $x'_i \neq x_i$ such that $f(x'_i, x_{-i})$ and $f(x_i, x_{-i})$ are different functions of $x_{-i}$. (on some measurable set)

\begin{theorem}
Let $p$ be a product probability distribution on $C=[0,1]^s$ so that $X_1,...,X_s$ are all independent. Let $f: C \rightarrow \R$ be a convex function, twice differentiable.

Suppose $f$ depends on all coordinates. Let $f_1,...,f_s \coloneqq \arg\min \{ \E | f(X) - \sum_k f_k(X_k) |^2 \,:\, \forall k, f_k \trm{ convex }, \E f_k(X_k) = 0\}$

 Then $f_1,...,f_s$ are non-constant functions.
 \end{theorem}

 \begin{lemma}
\label{lem:int_reduction}
Let $\mu$ be a probability measure on $C=[0,1]^s$. Let $f: C \rightarrow \R$ be a convex function, twice differentiable. Suppose that $\E f(X) = 0$.

Let $\ds f^*_1,...,f^*_s \coloneqq \arg\min \{ \E | f(X) - \sum_{k=1}^s f_k(X_k) |^2 \,:\, \forall k, f_k \trm{ convex }, \E f_k(X_k) = 0\}$ \\

Then $f^*_k(x_k) = \E[ f(X) | x_k]$.
\end{lemma}

@@

Fix $x_k$, we will show that the value $\E[ f(X) | x_k]$ minimizes 
\[
\min_{ f_k(x_k) } \int_{\mathbf{x}_{-k}} p(x) | f(\mathbf{x}) - \sum_{k' \neq k} f^*_{k'} (x_{k'}) - f_k (x_k)|^2 d \mathbf{x}_{-k}.
\]

Take the derivative with respect to $f_k(x_k)$ and set it equal to zero, we get that
\begin{align*}
\int_{\mathbf{x}_{-k}} p(\mathbf{x}) f_k(x_k) d \mathbf{x}_{-k} &= \int_{\mathbf{x}_{-k}} p(\mathbf{x}) ( f(\mathbf{x}) - \sum_{k' \neq k} f^*_{k'} (x_{k'}) ) d \mathbf{x}_{-k}  \\
p(x_k) f_k(x_k) &= \int_{\mathbf{x}_{-k}} p(\mathbf{x}) f(\mathbf{x}) d \mathbf{x}_{-k} 
 \end{align*}

Now, we verify that as a function of $x_k$, $\E[ f(X) | x_k]$ has mean zero and is convex. The former is true because $\E f(X) = 0$; the latter is true because for every $\mathbf{x}_{-k}$, $f(x_k, \mathbf{x}_{-k})$ is a convex function with respect to $x_k$ and therefore, $\int_{x_{-k}} p(\mathbf{x}|x_k) f(x_k, \mathbf{x}_{-k}) d \mathbf{x}_{-k}$ is still convex.

@@

 \begin{proposition}
Let $p$ be a product probability distribution on $C=[0,1]^s$ so that $X_1,...,X_s$ are all independent. Let $f: C \rightarrow \R$ be a convex function, twice differentiable.

@@

The first condition trivially implies the second because $\E f(X) = 0$.\\

Fix $k$. Suppose that, for all $x_k$, $\E[ f(X) | x_k] = 0$. \\

By the assumption that $p$ is a product measure, we know that, for all $x_k$,
\begin{align*}
p(x_k) \E[ f(X) | x_k ] &= \int_{\mathbf{x}_{-k}} p(\mathbf{x_{-k}} \,|\, x_k) f(x_k,\mathbf{x}_{-k}) d \mathbf{x}_{-k} \\
		&=  \int_{\mathbf{x}_{-k}} p(\mathbf{x_{-k}}) f(x_k,\mathbf{x}_{-k}) d \mathbf{x}_{-k} =0
\end{align*}

For every $\mathbf{x}_{-k}$, we define the derivative
\[
g(\mathbf{x}_{-k}) \coloneqq  \lim_{x_k \rightarrow 0^+} \frac{f(x_k, \mathbf{x}_{-k}) - f(0, \mathbf{x}_{-k})}{x_k}
\]
$g(\mathbf{x}_{-k})$ is well-defined by the assumption that $f$ is everywhere differentiable.\\

@@

Fact 1. By exchanging limit with the integral, we reason that 
\[
\int_{\mathbf{x}_{-k}} p(\mathbf{x}_{-k}) g(\mathbf{x}_{-k}) d \mathbf{x}_{-k} = 0
\]

@@

Because, for all $x_k, \mathbf{x}_{-k}$, 
\[
f(x_k, \mathbf{x}_{-k}) - f(0, \mathbf{x}_{-k}) - g(\mathbf{x}_{-k}) x_k \geq 0
\]
and
\[
\int_{\mathbf{x}_{-k}} p(\mathbf{x}_{-k}) (f(x_k, \mathbf{x}_{-k}) - f(0, \mathbf{x}_{-k}) - g(\mathbf{x}_{-k}) x_k) d\mathbf{x}_{-k} = 0
\]
we conclude that for all $x_k, \mathbf{x}_{-k}$, $f(x_k, \mathbf{x}_{-k}) = f(0, \mathbf{x}_{-k}) + g(\mathbf{x}_{-k}) x_k$.

@@

By proposition from Horn and Johnson [TODO ref], such a matrix is positive semidefinite if and only if the $k$-th row and column are also zero. \\

Since $k$-th row and column correspond precisely to the gradient of $g(\mathbf{x}_{-k})$, we conclude that $g$ must be a constant function. It follows therefore that $g = 0$ because it integrates to 0. \\

@@

\section{Deterministic Conditions}

\begin{theorem} (Deterministic) \\
The following holds regardless of whether we impose the boundness and smoothness condition in optimization~\ref{opt:alternate_opt} or not.\\

For $k \in \{1,...,p\}$, let $\Delta_{k, j}$ denote the $n$-dimensional vector $\max( X_k - X_{k (j)} \mathbf{1}, 0)$. \\

Let $\{\hat{d}_k, \hat{c}_k \}_{k \in S}$ be the minimizer of the restricted regression optimization program~\ref{opt:restricted_alternate_opt}. 
Let $\hat{d}_k = 0$ and $ \hat{c}_k = 0$ for $k \in S^c$.\\

Let $\hat{r} \coloneqq Y - \sum_{k \in S} (\Delta_k \hat{d}_k - \hat{c}_k \mathbf{1})$ be the residue.\\

@@

\begin{proof}
We will omit the boundness and smoothness constraints in our proof here. It is easy to add those in and check that the result of the theorem still holds.\\

@@

we can re-write the Lagrangian $L$, in term of just $d_k,c_k$, as the following.
\[
\min_{d_k, c_k}  \frac{1}{2n} \| r_k - \Delta_k d_k + c_k \mathbf{1} \|_2^2 + \lambda \sum_{i=2}^n d_{ki} + \lambda|d_{k1}| - \mu_k^\tran d_k + \gamma_k (c_k - \mathbf{1}^\tran\Delta_k d_k)
\]
where $r_k \coloneqq Y - \sum_{k \in S} (\Delta_k d_k - c_k \mathbf{1})$, and $\mu_k \in \R^n$ is a vector of dual variables where $\mu_{k,1} = 0$ and $\mu_{k,i} \geq 0$ for $i=2,...,n$.\\

First, note that by definition as solution of the restricted regression, for $k \in S$, $\hat{d}_k, \hat{c}_k$ satisfy stationarity with dual variables that satisfy complementary slackness. \\

@@

\begin{align*}
\partial d_k :& \qquad -\frac{1}{n} \Delta_k^\tran ( \hat{r} - \Delta_k \hat{d}_k - \hat{c}_k \mathbf{1}) + \lambda \mathbf{u}_k  - \mu_k - \gamma_k \Delta_k^\tran \mathbf{1} \\
\partial c_k: & \qquad -\frac{1}{n} \mathbf{1}^\tran ( \hat{r} - \Delta_k d_k - c_k \mathbf{1}) + \gamma_k
\end{align*}
In the derivatives, $\mathbf{u}$ is a $(n-1)$-vector whose first coordinate is $\partial | d_{k1}|$ and all other coordinates are 1.\\

@@

\begin{align*}
-\frac{1}{n} \Delta_k^\tran\hat{r} + \lambda \mathbf{u} - \mu_k - \gamma_k \Delta_k^\tran \mathbf{1} &= 0 \\
-\frac{1}{n} \mathbf{1}^\tran \hat{r} + \gamma_k & = 0 \\
\end{align*}
where $\mathbf{u}$ is 1 in every coordinate except the first, where it can take any value in $[-1,1]$.\\

@@

Suppose
\[
\lambda \mathbf{1} > |\frac{1}{n} \Delta_k^\tran\hat{r}|,
\]
then we easily see that the first coordinate of $\mathbf{u}$ can be set to some value in $(-1,1)$ and $\mu_{k,i} > 0$ for $i=2,...,n$. Because we have strict inequality, Lemma [TODO:get wainwright lemma] shows that all solutions must be zero on $S^c$.
\end{proof}

\subsection{Probabilistic Condition: Controlling False Positives}

\begin{theorem} (Probabilistic: Controlling False Positives) \\
Suppose assumptions A1, A2, A3 hold. Suppose also that we run optimization~\ref{opt:alternate_opt} with the $B$-boundness constraint.

Suppose $\lambda_n \geq c b (sB + \sigma) \sqrt{ \frac{s}{n} \log n \log (pn)}$, then with probability at least $ 1 - \frac{C}{n}$, for all $j,k$,
\[
\lambda_n >  | \frac{1}{n} \hat{r}^\tran \Delta_{k,j}|
\]
And therefore, the solution to the optimization~\ref{opt:alternate_opt}, with boundedness constraint, is zero on $S^c$.
\end{theorem}

\begin{proof}
The key is to note that $\hat{r}$ and $\Delta_{k,j}$ are independent for all $k,j$ because $\hat{r}$ is not a function of $X_{S^c}$ at all.

@@

\begin{align*}
\hat{r}_i &= Y_i - \sum_{k \in S} \hat{f}_k (X_k^{(i)}) \\
	&= f^*(X_S^{(i)}) + \epsilon_i - \bar{f^*} - \bar{\epsilon}- \sum_{k \in S} \hat{f}_k(X_k^{(i)}) \\
	&=  f^*(X_S^{(i)}) - \bar{f^*} - \sum_{k \in S} \hat{f}_k(X_k^{(i)}) + \epsilon_i - \bar{\epsilon}
\end{align*}
Where $\bar{f^*} = \frac{1}{n} \sum_{i=1}^n f^*(X_S^{(i)})$ and likewise for $\bar{\epsilon}$.\\

Suppose $\epsilon_i$ is subgaussian with subgaussian norm $\sigma$. For a single $\epsilon_i$, we have that $P( |\epsilon_i| \geq t ) \leq C \exp( - c \frac{1}{\sigma^2} t^2)$. Therefore, with probability at least $1-\delta$, $|\epsilon_i| \leq \sigma\sqrt{ \frac{1}{c} \log \frac{C}{\delta}}$.

By union bound, with probability at least $1-\delta$, $\max_i |\epsilon_i| \leq \sigma \sqrt{ \frac{1}{c} \log \frac{2nC}{\delta}}$.\\

Also, $|\bar{\epsilon}| \leq \sigma \sqrt{\frac{c}{n} \log \frac{C}{\delta}}$ with probability at least $1 - \delta$.\\

@@

We claim then that $F$ is coordinatewise-Lipschitz. Let $X = (X_1, X_2,...,X_n)$ and $X' = (X'_1, X_2, ..., X_n)$ differ only on the first coordinate. \\

@@

\subsection{Probabilistic Condition: Controlling False Negatives}

>>>>

\section*{Appendix}

\subsection{Proof of Additive Faithfulness}
\label{sec:faithful_proof}

We start with a lemma similar to Lemma~\ref{lem:general_int_reduction} and whose proofs are identical.

\begin{lemma}
\label{lem:int_reduction}
Let $F$ be a product distribution on $C=[0,1]^s$ with density function $p$. Let $f: C \rightarrow \R$ be a convex function. Suppose that $\E f(X) = 0$.

Let $\ds f^*_1,...,f^*_s \coloneqq \arg\min \{ \E | f(X) - \sum_{k=1}^s f_k(X_k) |^2 \,:\, \forall k, f_k \trm{ convex }, \E f_k(X_k) = 0\}$

Then $f^*_k(x_k) = \E[ f(X) \given x_k]$.
\end{lemma}

@@

Fix $x_k$, we will show that the value $\E[ f(X) | x_k]$, for all $x_k$,  uniquely minimizes 
\[
\min_{ f_k(x_k) } \int_{\mathbf{x}_{-k}} p(x) | f(\mathbf{x}) - \sum_{k' \neq k} f^*_{k'} (x_{k'}) - f_k (x_k)|^2 d \mathbf{x}_{-k}.
\]
If this is true, then the function $x_k \mapsto \E[ f(X) \given x_k]$ is the unique $f^*_k(x_k)$ that minimizes the expected square error.

Take the derivative with respect to the value $f_k(x_k)$ and set it equal to zero, we get that
\begin{align*}
\int_{\mathbf{x}_{-k}} p(\mathbf{x}) f_k(x_k) d \mathbf{x}_{-k} &= \int_{\mathbf{x}_{-k}} p(\mathbf{x}) ( f(\mathbf{x}) - \sum_{k' \neq k} f^*_{k'} (x_{k'}) ) d \mathbf{x}_{-k} \\  
   p(x_k) f_k(x_k) &= p(x_k) \int_{\mathbf{x}_{-k}} p(\mathbf{x}_{-k}) ( f(\mathbf{x}) - \sum_{k' \neq k} f^*_{k'} (x_{k'}) ) d \mathbf{x}_{-k} \\
f_k(x_k) &= \int_{\mathbf{x}_{-k}} p(\mathbf{x}_{-k}) f(\mathbf{x}) d \mathbf{x}_{-k} 
 \end{align*}
Where the second line follows because $p(\mathbf{x}) = \prod_k p(x_k)$ by product distribution assumption. The third line follows because $\int_{\mathbf{x}_{-k}} p(\mathbf{x}_{-k}) f^*_{k'}(x_{k'}) d\mathbf{x}_{-k} = 0$ for all $k' \neq k$ by the constraint that $\E[f^*_{k'}(X_{k'})] = 0$.

The square error objective is strongly convex. The second derivative with respect to $f_k(x_k)$ is $2 p(x_k)$, which is always positive under the assumption that $p$ is positive. Therefore, the solution $f^*_k(x_k) = \E[ f(X) \given x_k ]$ is unique.

Now, we verify that as a function of $x_k$, $\E[ f(X) | x_k]$ has mean zero and is convex. The former is true because $\E f(X) = 0$; the latter is true because for every $\mathbf{x}_{-k}$, $f(x_k, \mathbf{x}_{-k})$ is a convex function with respect to $x_k$ and therefore, $\int_{\mathbf{x}_{-k}} p(\mathbf{x}_{-k}) f(x_k, \mathbf{x}_{-k}) d \mathbf{x}_{-k}$ is still convex.

@@

 The next proposition, combined with the previous Lemma, proves Theorem~\ref{thm:convex_faithful}.

 \begin{proposition}
Let $F$ be a product distribution supported on $C=[0,1]^s$ with positive density $p > 0$. Let $f: C \rightarrow \R$ be a convex function, twice differentiable.

@@

The first condition trivially implies the second because $\E f(X) = 0$.

Fix $k$. Suppose that, for all $x_k$, $\E[ f(X) | x_k] = 0$.

By the assumption that , we know that, for all $x_k$,
\begin{align*}
p(x_k) \E[ f(X) | x_k ] &=  \int_{\mathbf{x}_{-k}} p(\mathbf{x_{-k}}) f(x_k,\mathbf{x}_{-k}) d \mathbf{x}_{-k} =0
\end{align*}

For every $\mathbf{x}_{-k}$, we define the derivative
\[
g(\mathbf{x}_{-k}) \coloneqq  \lim_{x_k \rightarrow 0^+} \frac{f(x_k, \mathbf{x}_{-k}) - f(0, \mathbf{x}_{-k})}{x_k}
\]
$g(\mathbf{x}_{-k})$ is well-defined by the assumption that $f$ is everywhere differentiable.

@@

Fact 1. By exchanging limit with the integral, which is valid by bounded convergence theorem, we reason that 
\[
\int_{\mathbf{x}_{-k}} p(\mathbf{x}_{-k}) g(\mathbf{x}_{-k}) d \mathbf{x}_{-k} = 0
\]

@@

For all $x_k, \mathbf{x}_{-k}$, 
\[
f(x_k, \mathbf{x}_{-k}) - f(0, \mathbf{x}_{-k}) - g(\mathbf{x}_{-k}) x_k \geq 0
\]
and
\[
\int_{\mathbf{x}_{-k}} p(\mathbf{x}_{-k}) (f(x_k, \mathbf{x}_{-k}) - f(0, \mathbf{x}_{-k}) - g(\mathbf{x}_{-k}) x_k) d\mathbf{x}_{-k} = 0
\]
Since $f(x_k, \mathbf{x}_{-k}) - f(0, \mathbf{x}_{-k}) - g(\mathbf{x}_{-k}) x_k$ is a continuous function of $\mathbf{x}_{-k}$ and the density $p(\mathbf{x}_{-k})$ is, by assumption, non-zero on the support, we conclude that for all $x_k, f(x_k, \mathbf{x}_{-k}) - f(0, \mathbf{x}_{-k}) - g(\mathbf{x}_{-k}) x_k =0 $ necessarily and thus $\mathbf{x}_{-k}$, $f(x_k, \mathbf{x}_{-k}) = f(0, \mathbf{x}_{-k}) + g(\mathbf{x}_{-k}) x_k$.

@@

By proposition 7.1.10 from Horn and Johnson~\cite{HJ90},  such a matrix is positive semidefinite if and only if the $k$-th row and column are also zero. (to prove this, one can first work with a 2 by 2 matrix and then use the fact that every principal submatrix of a PSD matrix must be PSD)

Since $k$-th row and column correspond precisely to the gradient of $g(\mathbf{x}_{-k})$, we conclude that $g$ must be a constant function. It follows therefore that $g = 0$ because it integrates to 0.

@@

 \subsection{Proof of the Deterministic Condition for Sparsistency}
 \label{sec:deterministic_proof}

 We restate Theorem~\ref{thm:deterministic} first for convenience.

\begin{theorem} 
The following holds regardless of whether we impose the boundness and smoothness condition in optimization~\ref{opt:alternate_opt} or not.

For $k \in \{1,...,p\}$, let $\Delta_{k, j}$ denote the $n$-dimensional vector $\max( X_k - X_{k (j)} \mathbf{1}, 0)$.

Let $\{\hat{d}_k, \hat{c}_k \}_{k \in S}$ be the minimizer of the restricted regression optimization program~\ref{opt:alternate_opt}. 
Let $\hat{d}_k = 0$ and $ \hat{c}_k = 0$ for $k \in S^c$.

Let $\hat{r} \coloneqq Y - \sum_{k \in S} (\Delta_k \hat{d}_k - \hat{c}_k \mathbf{1})$ be the residue.

@@

\begin{proof}
We will omit the boundness and smoothness constraints in our proof here. It is easy to add those in and check that the result of the theorem still holds.

@@

we can re-write the Lagrangian $L$, in term of just $d_k,c_k$, as the following.
\[
\min_{d_k, c_k}  \frac{1}{2n} \| r_k - \Delta_k d_k + c_k \mathbf{1} \|_2^2 + \lambda \sum_{i=2}^n d_{ki} + \lambda|d_{k1}| - \mu_k^\tran d_k + \gamma_k (c_k - \mathbf{1}^\tran\Delta_k d_k)
\]
where $r_k \coloneqq Y - \sum_{k' \in S, k' \neq k} (\Delta_{k'} d_{k'} - c_{k'} \mathbf{1})$, and $\mu_k \in \R^n$ is a vector of dual variables where $\mu_{k,1} = 0$ and $\mu_{k,i} \geq 0$ for $i=2,...,n$.

First, note that by definition as solution of the restricted regression, for $k \in S$, $\hat{d}_k, \hat{c}_k$ satisfy stationarity with dual variables that satisfy complementary slackness.

@@

\begin{align*}
\partial d_k :& \qquad -\frac{1}{n} \Delta_k^\tran ( \hat{r} - \Delta_k \hat{d}_k + \hat{c}_k \mathbf{1}) + \lambda \mathbf{u}_k  - \mu_k - \gamma_k \Delta_k^\tran \mathbf{1} \\
\partial c_k: & \qquad -\frac{1}{n} \mathbf{1}^\tran ( \hat{r} - \Delta_k d_k + c_k \mathbf{1}) + \gamma_k
\end{align*}
In the derivatives, $\mathbf{u}$ is a $(n-1)$-vector whose first coordinate is $\partial | d_{k1}|$ and all other coordinates are 1.

@@

\begin{align*}
-\frac{1}{n} \Delta_k^\tran\hat{r} + \lambda \mathbf{u} - \mu_k - \gamma_k \Delta_k^\tran \mathbf{1} &= 0 \\
-\frac{1}{n} \mathbf{1}^\tran \hat{r} + \gamma_k & = 0 \\
\end{align*}
where $\mathbf{u}$ is 1 in every coordinate except the first, where it can take any value in $[-1,1]$.

@@

Suppose
\[
\lambda \mathbf{1} > |\frac{1}{n} \Delta_k^\tran\hat{r}|,
\]
then we easily see that the first coordinate of $\mathbf{u}$ can be set to some value in $(-1,1)$ and we can set $\mu_{k,i} > 0$ for $i=2,...,n$.

Because we have strict inequality in the above equation, Lemma 1 from ~\cite{Wain:09a} show that all solutions must be zero on $S^c$.
\end{proof}

 \subsection{Proof of False Positive Control}
 \label{sec:false_positive_proof}

 We first restate the theorem for convenience.

\begin{theorem} 
Suppose assumptions A1, A2, A3 hold.

Suppose $\lambda_n \geq c b (sB + \sigma) \sqrt{ \frac{s}{n} \log n \log (pn)}$, then with probability at least $ 1 - \frac{C}{n}$, for all $j,k$,
\[
\lambda_n >  | \frac{1}{n} \hat{r}^\tran \Delta_{k,j}|
\]
And therefore, the solution to the optimization~\ref{opt:alternate_opt} is zero on $S^c$.
\end{theorem}

\begin{proof}
The key is to note that $\hat{r}$ and $\Delta_{k,j}$ are independent for all $k,j$ because $\hat{r}$ is only dependent on $X_{S}$.

@@

\begin{align*}
\hat{r}_i &= Y_i - \sum_{k \in S} \hat{f}_k (X_k^{(i)}) \\
	&= f^*(X_S^{(i)}) + \epsilon_i - \bar{f^*} - \bar{\epsilon}- \sum_{k \in S} \hat{f}_k(X_k^{(i)}) \\
	&=  f^*(X_S^{(i)}) - \bar{f^*} - \sum_{k \in S} \hat{f}_k(X_k^{(i)}) + \epsilon_i - \bar{\epsilon}
\end{align*}
Where $\bar{f^*} = \frac{1}{n} \sum_{i=1}^n f^*(X_S^{(i)})$ and likewise for $\bar{\epsilon}$.

$\epsilon_i$ is subgaussian with subgaussian norm $\sigma$. For a single $\epsilon_i$, we have that $P( |\epsilon_i| \geq t ) \leq C \exp( - c \frac{1}{\sigma^2} t^2)$. Therefore, with probability at least $1-\delta$, $|\epsilon_i| \leq \sigma\sqrt{ \frac{1}{c} \log \frac{C}{\delta}}$.

By union bound, with probability at least $1-\delta$, $\max_i |\epsilon_i| \leq \sigma \sqrt{ \frac{1}{c} \log \frac{2nC}{\delta}}$.

Also, $|\bar{\epsilon}| \leq \sigma \sqrt{\frac{c}{n} \log \frac{C}{\delta}}$ with probability at least $1 - \delta$.

@@

We claim then that $F$ is coordinatewise-Lipschitz. Let $X = (X_1, X_2,...,X_n)$ and $X' = (X'_1, X_2, ..., X_n)$ differ only on the first coordinate.

@@

 \subsection{Proof of False Negative Control}
 \label{sec:false_negative_proof}
